%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\vspace{-0.3cm}
\begin{small}\textit{* presenting author}\end{small}%; \textsuperscript{+} mentored undergraduate}\end{small}

%-------------------------------------------------------------------------------
\cvsubsection{Invited Talks}
%-------------------------------------------------------------------------------

\begin{cvpubs}

    \cvpub{Fulton, E.*,  Boschetti, F.* \& \textbf{Andreotta, M.}* (2024). \textit{Challenges in ocean research---how might art help?}. Presented for the Lawrence Wilson Art Gallery, University of Western Australia.}

    \cvpub{Cavve, B.* \& \textbf{Andreotta, M.}* (2023). \textit{Science is a liar (sometimes): Questionable practices in research and communication}. Presented for Telethon Kids Institute.}

    \cvpub{\textbf{Andreotta, M.}* (2023). \textit{The psychological roots of the rejection (and acceptance) of science}. Presented for Centre for Marine Socioecology.}

    \cvpub {\textbf{Andreotta, M.}* (2019). \textit{Analysing social media: A mixed-methods framework for combining computational and text analysis}. Presented for Data61, Commonwealth Scientific and Industrial Research Organisation (CSIRO), Sydney, Australia.}
    
    \cvpub{\textbf{Andreotta, M.}* (2019). \textit{Tweeting about climate change: Blending data science and psychology to analyse social media}. Guest Speaker for ENVT2221 (Global Climate Change and Biodiversity), University of Western Australia.}
    
    \cvpub{\textbf{Andreotta, M.}* (2019). \textit{Tweeting about climate change: Blending data science and psychology to analyse social media}. Presented for Oceans \& Atmosphere, Commonwealth Scientific and Industrial Research Organisation (CSIRO), Perth, Australia.}
    
    \cvpub{\textbf{Andreotta, M.}* \& Cavve, B.* (2018 \& 2019). \textit{Science is a liar (sometimes): Questionable practices in research and communication}. Guest Speaker for PSYC3303 (Psychological Science in the Modern World), University of Western Australia.}
    
    \cvpub{\textbf{Andreotta, M.}* \& Wang, S.* (2016). \textit{It's (not) about climate change}. Guest Speaker for PSYC3303 (Psychological Science in the Modern World), University of Western Australia.}
\end{cvpubs}

%-------------------------------------------------------------------------------
\cvsubsection{Conference Presentations}
%-------------------------------------------------------------------------------

\begin{cvpubs}
    \cvpub{\textbf{Andreotta, M.}*, Paris, C., van Putten, I., Hurlstone, M. J., Walker, I., \& Boschetti, F. (2023). \textit{Detecting and responding to moralised misinformation}. Presented at the Understanding and Countering Mis/Disinformation Workshop, Melbourne, Australia.}

    \cvpub{\textbf{Andreotta, M.}* (2019). \textit{Analysing social media: A mixed-methods framework for combining computational and text analysis}. Presented at the Australasian Mathematical Psychology Conference, Melbourne, Australia.}

    %\cvpub{Undergrad, Y*\textsuperscript{+}, \textbf{Your Name}, Author Three, Author Four. 2015. Title of a poster presented by an undergrad I mentored. Poster: Event Presented At, City, State.}
\end{cvpubs}
