%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\begin{minipage}{\textwidth}
\cvsection{Teaching Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {PSYC3303: Psychological Science in the Modern World} % Course
    {Tutor.\linebreak
    This unit provides students with psychological theories, methods, and evidence for understanding and solving contemporary social problems. Additionally, students are taught the skills necessary to communicate science to key stakeholders. The topics of the unit vary year to year as key social issues and psychological evidence change. I was responsible for developing and delivering tutorials to equip students with knowledge of psychological theory and evidence, as well as the skills to think critically and communicate to laypeople and stakeholders. I have delivered several guest lectures for the unit. In 2016, I delivered a lecture providing cognitive psychological insights into the apparent inconsistencies of public perceptions on climate change. In later years, I delivered a lecture equipping students with critical thinking skills to examine science and science communication.
    } % Course
    {University of Western Australia} % Location
    {2016-2019} % Date(s)


%---------------------------------------------------------
  \cvhonor
    {PSYC 3310: Specialist Research Methods (Behavioural Economics)} % Course
    {Tutor.\linebreak
    This unit provides students with the opportunity to learn about and perform research in a specialist topic area of psychology. Students are provided with seminars on psychological theories, methods, and evidence of a topic area, as well as skill-orientated tutorials. I tutored a class on behavioural economics research. As a tutor, I was responsible for teaching students to prepare ethics applications, prepare research proposals, design and run studies, analyse data, and prepare research reports.
    } % Position
    {University of Western Australia} % Location
    {2018} % Date(s)

%---------------------------------------------------------
\end{cvhonors}
\end{minipage}

