%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Service and Outreach} %\& Professional Development}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\cvsubsection{Outreach}
\begin{cvhonors}
%---------------------------------------------------------

  \cvhonor
    {Lawrence Wilson Art Gallery Event for High-School Students, University of Western Australia} % Event/Organization
    {Presented an interactive behavioural economics activity.} % Position
    {} % Location
    {2024} % Date(s)
    
  \cvhonor
    {School of Indigenous Study's Science Camp for High-School Students, University of Western Australia} % Event/Organization
    {Presenter.} % Position
    {} % Location
    {2019} % Date(s)
    
%---------------------------------------------------------
  \cvhonor
    {School of Psychological Science's \textit{Psyched@UWA} Event for High-School Students, University of Western Australia} % Event/Organization
    {Presented an interactive behavioural economics activity.} % Position
    {} % Location
    {} % Date(s)
    
    \cvhonor
    {ASPIRE Camp for High-School Students, University of Western Australia} % Event/Organization
    {Presented an interactive behavioural economics activity.} % Position
    {} % Location
    {} % Date(s)

    
\end{cvhonors}
\begin{minipage}{\textwidth}
\cvsubsection{Service}
\begin{cvhonors}
%---------------------------------------------------------
    
%---------------------------------------------------------

  \cvhonor
    {Committee Member} % Position
    {Early- and Mid-Career Researcher Committee, CSIRO Environment.} % Event/Organization
    {} % Location
    {2022-2025} % Date(s)


  \cvhonor
    {Post-graduate Representative} % Position
    {Working Group on Addressing and Resolving Conflicts with Supervisors, School of Psychological Science, University of Western Australia.} % Event/Organization
    {} % Location
    {2019} % Date(s)
    
    \cvhonor
    {Committee Member} % Position
    {Working Group on Gendered Discrimination and Misconduct, School of Psychological Science, University of Western Australia.} % Event/Organization
    {} % Location
    {} % Date(s)
    
    \cvhonor
    {Co-director} % Position
    {OpenLab, School of Psychological Science, University of Western Australia.
    A student-led group to disseminate research and learn about open-science principles.} % Event/Organization
    {} % Location
    {} % Date(s)    
    
    \cvhonor
    {Assisted in Operations} % Position
    {Pint of Science, Perth, Western Australia.
    } % Event/Organization
    {} % Location
    {} % Date(s)  
    \end{cvhonors}
    \end{minipage}
    
    \begin{cvhonors}
    
    
    \cvhonor
    {Assisted in Conference Operations} % Position
    {Australasian Mathematical Psychology Conference, Perth, Western Australia, Australia.} % Event/Organization
    {} % Location
    {2018} % Date(s)
      
    \cvhonor
    {Post-graduate Representative} % Position
    {Gender Diversity Panel, School of Psychological Science, University of Western Australia.} % Event/Organization
    {} % Location
    {2017} % Date(s)


    
\end{cvhonors}
\begin{minipage}{\textwidth}
\cvsubsection{Peer Review}

\begin{small} \color{black}
I am an ad hoc reviewer for \textit{Behavior Research Methods} and \textit{Environmental Science and Policy}.
\end{small}
\end{minipage}

%\cvsubsection{Professional Memberships}

%\begin{small} \color{black}
%One fancy society \\
%Another fancy society \\
%\end{small}
