%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Awards, Fellowships, \& Grants}

%-------------------------------------------------------------------------------
%	2018
%-------------------------------------------------------------------------------
\cvsubsection{Awards}
%---------------------------------------------------------

\begin{cvhonors}
    \cvhonor
    {Responsible Innovation Project Call}
    {Commonwealth Scientific and Industrial Research Organisation.\linebreak
    Awarded for the project: \textit{Low conflict pathways to renewable energy: using predictive models to reduce social risk}} % Awarding Organization
    {\$ \ 298,000} % Amount -- leave blank if not including amounts
    {2023} % Date(s)
    \cvhonor
    {Sustainability Research Grant}
    {Lancaster University.\linebreak
    Awadred for the project: \textit{Moral determinants of support for, and opposition to, climate activism}} % Awarding Organization
    {\pounds\ 10,000} % Amount -- leave blank if not including amounts
    {} % Date(s)
    \cvhonor
    {Outreach initiative}
    {Lawrence Wilson Art Gallery, University of Western Australia.\linebreak
    Awarded for the project: \textit{The Ocean Project} to communicate complex ideas relating to the ocean} % Awarding Organization
    {\$ \ 5,000} % Amount -- leave blank if not including amounts
    {} % Date(s)
\end{cvhonors}
%---------------------------------------------------------


\begin{cvhonors}
    \cvhonor
    {Graduate Research School’s Publication Award}
    {University of Western Australia.\linebreak
    A yearly award issued for the best Quantitative Social Science publication by a higher degree student.
    Awarded for: \textit{Analyzing social media data: A mixed-methods framework combining computational and qualitative text analysis}.} % Awarding Organization
    {\$ 500} % Amount -- leave blank if not including amounts
    {2020} % Date(s)
\end{cvhonors}
%---------------------------------------------------------
\begin{cvhonors}
  \cvhonor
    {Research on Research Integrity Grant} %Awards
    {Office of Research Integrity, U.S. Department of Health and Human Services.\linebreak
    Awarded for the project: \textit{Evaluation of Twitter as a post-publication peer review mechanism to identify responsible conduct of research concerns}.
    }
    {\$ 139,183} % Amount
    {2019} % Date(s)
\end{cvhonors}
%---------------------------------------------------------
\begin{cvhonors}
%---------------------------------------------------------
  \cvhonor
    {Postgraduate Top-Up Scholarship for ``Gaining insights from social networks''} % Award
    {Data61, Commonwealth Scientific and Industrial Research Organisation.} % Awarding Organization
    {\$ 51,000} % Amount
    {2016} % Date(s)
%---------------------------------------------------------
  \cvhonor
    {Research Training Program Stipend} % Award
    {Department of Education, Skills and Employment.} % Awarding Organization
    {\$ 105,000} % Amount
    {} % Date(s)
\end{cvhonors}

