%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\cvsubsection{Peer-Reviewed Manuscripts - Published or In Press}
%---------------------------------------------------------

\begin{cvpubs}

    \cvpub{\textbf{Andreotta, M.}, Mocatta, G., Lubicz-Zaorski, C., Morrison, T. H., van Putten, I., \& Pecl, G. (in press). Steering Great Barrier Reef climate science narratives through the mediasphere in a time of misinformation. \textit{npj Climate Action}.}

    \cvpub{Spillias, S., Ollerhead, K. M., \textbf{Andreotta, M.}, Annand-Jones, R., Boschetti, F., Duggan, J., Karcher, D., Paris, C., Shellock, R. J., \& Trebilco, R. (2025). Evaluating generative AI for qualitative data extraction in community-based fisheries management literature. \textit{Environmental Evidence}, \textit{14}(9).}

    \cvpub{Spillias, S., Paris, T., \textbf{Andreotta, M.}, Annand-Jones, R., Boschetti, F., Cvitanovic, C., Duggan, J., Fulton, E., Karcher, D., Paris, C., Shellock, R., \& Trebilco, R. (2024). Human-AI Collaboration to identify literature for evidence synthesis. \textit{Cell Reports Sustainability}.}

    \cvpub{Atee, M., \textbf{Andreotta, M.}, Lloyd, R., Whiting, D., Alford, M., \& Morris, T. (2023). Does pain matter in the Australian Royal Commission into Aged Care Quality and Safety? A text mining study. \textit{Aging and Health Research}, \textit{3}(1)., 1-6}

    \cvpub{\textbf{Andreotta, M.}, Boschetti, F., Farrell, S., Paris, C., Walker, I., \& Hurlstone, M. J. (2022). Evidence for three distinct climate change audience segments with varying belief updating tendencies: Implications for climate change communication. \textit{Climatic Change}, \textit{174}(32), 1-29.}

    \cvpub{Atee, M., \textbf{Andreotta, M.}, Morris, T., \& Alford, M. (2022). Psychotropic polypharmacy in people with neuropsychiatric symptoms referred to an Australian dementia support service. \textit{Alzheimer\'s \& Dementia}, \textit{18}, 1.}

    \cvpub{Calder, S., \textbf{Andreotta, M.}, Morris, T., \& Atee, M. (2022). Improving quality in pastoral care using the Pastoral Care Activity Tracker (PCAT): A feasibility study of a digital tool within an Australian healthcare organization. \textit{Journal of Health Care Chaplaincy}, 1-16.}

    \cvpub{Ecker, U. K. H., Sze, B. K. N., \& \textbf{Andreotta, M.} (2021). Corrections of political misinformation: No evidence for an effect of partisan worldview in a U.S. convenience sample. \textit{Philosophical Transactions of the Royal Society B}, \textit{376}(1822), 1-8.}
    
    \cvpub{\textbf{Andreotta, M.}, Nugroho, R., Hurlstone, M. J., Boschetti, F., Farrell, S., Walker, I., \& Paris, C. (2019). [Contribution to special issue on ``Using Big Data to Discover Principles of Cognition''] Analyzing social media data: A mixed-methods framework combining computational and qualitative text analysis. \textit{Behavior Research Methods}, \textit{51}(4), 1766–1781.}

    \cvpub{Boschetti, F., \& \textbf{Andreotta, M}. (2017). Mental models, communication, and engagement in marine projects. \textit{ICES Journal of Marine Science}, \textit{74}(7), 2034–2039.}
    
\end{cvpubs}


\begin{minipage}{\textwidth}
% %---------------------------------------------------------
\cvsubsection{Letters to the Editor - Published or In Press}
% %---------------------------------------------------------
\begin{cvpubs}
    \small \color{black}
    
    \cvpub{\textbf{Andreotta, M.}, Atee, M., Morris, T., \& Alford, M. (2022). Comments on Westera et al. (2022), ``Support for people with dementia experiencing severe responsive behaviours: Unpacking the disconnect between policy and practice''. \textit{Australasian Journal on Ageing}, 1-2.}
\end{cvpubs}
\end{minipage}


% %---------------------------------------------------------
%\cvsubsection{In Review}
% %---------------------------------------------------------

%\begin{cvpubs}
%    \cvpub{Manuscript 1}
%
%    \cvpub{Manuscript 2}
%\end{cvpubs}

\begin{minipage}{\textwidth}

% %---------------------------------------------------------
\cvsubsection{Selected Manuscripts - Submitted or In Preparation}
% %---------------------------------------------------------
\begin{cvpubs}
\small \color{black}

    \cvpub{\textbf{Andreotta, M.}, Boschetti, F., Farrell, S., Paris, C., Walker, I., \& Hurlstone, M. J. (\the\year{}, in preparation). Does extreme climate event exposure influence climate-related opinions? The case of the 2019--2020 Australian Black Summer bushfires.}

    \cvpub{\textbf{Andreotta, M.}, Condie, C., Boschetti, F., \& Condie, S. (\the\year{}, in preparation). GPT often, but not always, outperforms simple methods for classifying sentiment.}

    \cvpub{Hori, J., \textbf{Andreotta, M.}, Makino, M., Lew, D., Boschetti, F., Thébaud, O., Leonardi, S., Krien N., (\the\year{}, in preparation). The characteristics and antecedents of global ocean attitudes.}
    
%    \cvpub{Jellison, S., \textbf{Andreotta, M.}, Cooper, C., Paris, P., Nugroho, R., \& Vassar, M. (\the\year{}, in preparation). The use of Twitter in the Post Publication Peer Review process.}

 %   \cvpub{Mortimer, M., Rossen, I., \textbf{Andreotta, M.}, Dunlop, P., \& Hurlstone, M. J. (\the\year{}, in preparation). Accepters, fence sitters, or rejecters revisited: Converging evidence for different moral profiles of vaccination attitudes.}
\end{cvpubs}
\end{minipage}

% %---------------------------------------------------------
