%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Technical Skills}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
%---------------------------------------------------------
\begin{small} \color{black}

I have eight years of experience using \textit{R} and \LaTeX to produce manuscripts for scientific journals. I am experienced with other programming languages, such as \textit{Python}, \textit{JavaScript}, and \textit{MATLAB}, as well as popular statistical programs used in psychology, such as \textit{SPSS} and \textit{JASP}. I am proficient with tools for data storage and sharing, such as \textit{Git}, \textit{Apache Arrow} and \textit{MySQL}, as well as data repositories, such as \textit{Github}, \textit{Bitbucket}, and the \textit{Open Science Framework}.

I am well-versed in experimental and survey research designs. For example, my understanding of \textit{Qualtrics}, \textit{JavaScript}, and \textit{R} has allowed me to code complex experiments and custom Internet interfaces for online studies. I am experienced with hosting custom and secure web applications on servers, with the use of virtualisation software (that is, \textit{Docker}). Additionally, I am experienced with the automated collection of Internet data, through the use of Application Programming Interfaces or web scraping.

Broadly, I am skilled with quantitative, qualitative, and mixed-methods research approaches. Regarding quantitative techniques, I am competent with methods to handle large and complex data, such as mixed-effects modelling, regression analyses (e.g., ridge and lasso), and bootstrapping methods. I can use natural language processing techniques to model text data, such as the identification of sentiment, emotions, moral language, and topics. Concerning qualitative techniques, I am experienced in text analysis, such as thematic analysis and content analysis. Lastly, I have expertise in blending quantitative and qualitative analyses under mixed-methods frameworks, such as my four-phased framework \parencite{andreotta2019} and integrating insights from quantitative survey data with insights from text responses to open-ended questions.

\cvsubsection{References}

\printbibliography[heading=none]

\end{small}

%---------------------------------------------------------
