%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\cvsubsection{Peer Reviewed Manuscripts - Published or In Press}
%---------------------------------------------------------

\begin{cvpubs}
    \cvpub{Ecker, U. K. H., Sze, B. K. N., \& \textbf{Andreotta, M.} (in press). Corrections of political misinformation: No evidence for an effect of partisan worldview in a U.S. convenience sample. \textit{Philosophical Transactions of the Royal Society B}.}
    
    \cvpub{\textbf{Andreotta, M.}, Nugroho, R., Hurlstone, M. J., Boschetti, F., Farrell, S., Walker, I., \& Paris, C. (2019). [Contribution to special issue on ``Using Big Data to Discover Principles of Cognition''] Analyzing social media data: A mixed-methods framework combining computational and qualitative text analysis. \textit{Behavior Research Methods}, \textit{51}(4), 1766–1781.}

    \cvpub{Boschetti, F., \& \textbf{Andreotta, M}. (2017). Mental models, communication, and engagement in marine projects. \textit{ICES Journal of Marine Science}, \textit{74}(7), 2034–2039.}
\end{cvpubs}

% %---------------------------------------------------------
%\cvsubsection{In Review}
% %---------------------------------------------------------

%\begin{cvpubs}
%    \cvpub{Manuscript 1}
%
%    \cvpub{Manuscript 2}
%\end{cvpubs}
\begin{minipage}{\textwidth}
% %---------------------------------------------------------
\cvsubsection{Peer Reviewed Manuscripts - In Preparation}
% %---------------------------------------------------------

\begin{cvpubs}
\small \color{black}

    \cvpub{\textbf{Andreotta, M.}, Boschetti, F., Farrell, S., Paris, C., Walker, I., \&  Hurlstone, M. J. (2021, in preparation). Evidence for three distinct climate change audience segments with varying belief updating tendencies: Implications for climate change communication.}
    
    \cvpub{Jellison, S., \textbf{Andreotta, M.}, Cooper, C., Paris, P., Nugroho, R., \& Vassar, M. (2021, in preparation). The use of Twitter in the Post Publication Peer Review process.}

    \cvpub{Mortimer, M., Rossen, I., \textbf{Andreotta, M.}, Dunlop, P., \& Hurlstone, M. J. (2021, in preparation). Accepters, fence sitters, or rejecters revisited: Converging evidence for different moral profiles of vaccination attitudes.}

\end{cvpubs}
\end{minipage}

% %---------------------------------------------------------
