%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Technical Skills}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
%---------------------------------------------------------
\begin{small} \color{black}


I am a proficient user of \textit{R} and \textit{\LaTeX}. I am competent with \textit{SPSS} and \textit{JASP}. I have experience with \textit{Python}, \textit{JavaScript}, and \textit{MATLAB}. I am proficient with tools for data storage and sharing, such as \textit{Git} and \textit{MySQL}, as well as data repositories, such as \textit{Github}, \textit{Bitbucket}, and the \textit{Open Science Framework}.

I am proficient with experimental and survey designs. My understanding of \textit{Qualtrics}, \textit{JavaScript}, and \textit{R} has allowed me to code complex experiments and custom Internet interfaces for online studies. I am experienced with hosting custom web applications on servers, with the use of virtualisation software (that is, \textit{Docker}). Additionally, I am experienced with the collection of Twitter data.

I am proficient with quantitative, qualitative, and mixed-methods approaches. Regarding quantitative techniques, I am competent with methods to handle large and complex data, such as mixed-effects modelling, regression analyses (e.g., ridge and lasso), and bootstrapping methods. I have experience with some data science analyses, such as topic modelling. Concerning qualitative techniques, I am experienced in analysis of text data, such as thematic analysis and content analysis. Lastly, I have expertise in blending quantitative and qualitative analyses under mixed-methods frameworks, such as my four-phased framework \parencite{andreotta2019} and integrating insights from quantitative survey data with insights from text responses to open-ended questions.

\cvsubsection{References}

\printbibliography[heading=none]

\end{small}

%---------------------------------------------------------
